Inference of seasonal forcings on reproduction numbers during epidemics

### 2020-04-18 PaperDraft.Rmd
Remove unnecessary Thompson fit results

To avoid the model ascribing deviations in $R$ to the seasonal forcings without
widespread evidence across locations and times, three other features of our
model are the parameters $\theta(t)$, $\lambda_i$, and $\varepsilon_i(t)$. The
first parameter, $\theta(t)$, describes the logarithm country-wide $R$ before
adjusting for location and climate and local idiosyncratic factors. That is, it
can be thought of as a baseline $R$ value affected simply by the national
circumstances at the given time; such as national policies or human behavioral
changes. This will encapsulate various unmodeled behaviours such as weekends or
interventions. At time zero, our prior belief is that this $R$ will match the
consensus of international estimates for $R_0$, which vary widely but tend to
cluster between $2$ or $3$ [TK: Citation needed?]. Because of the great
uncertainty, there is significant variance in this assumption, so the prior is
quite weak (note that the $\mu \pm 2\sigma$ values, when transformed
exponentially, are below $1$ and above $6$ respectively).

@@

```{r include=FALSE}
```

>>>>

To avoid the model ascribing deviations in $R$ to the seasonal forcings without
widespread evidence across locations and times, three other features of our
model are the parameters $\theta(t)$, $\lambda_i$, and $\varepsilon_i(t)$. The
first parameter, $\theta(t)$, describes the logarithm country-wide $R$ before
adjusting for location and climate and local idiosyncratic factors. That is, it
can be thought of as a baseline $R$ value affected simply by the national
circumstances at the given time; such as national policies or human behavioral
changes. This will encapsulate various unmodeled behaviours such as weekends or
interventions. At time zero, our prior belief is that this $R$ will match the
consensus of international estimates for $R_0$, which vary widely but tend to
cluster between $2$ or $3$. Because of the great
uncertainty, there is significant variance in this assumption, so the prior is
quite weak (note that the $\mu \pm 2\sigma$ values, when transformed
exponentially, are below $1$ and above $6$ respectively).

@@

```{r include=FALSE}
require(cfc19i)

res <- results()
```
